\documentclass{article}
\usepackage{ketpic,ketlayer}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{bm,enumerate}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\setmargin{20}{20}{20}{20}

\renewcommand{\labelitemi}{$\cdot$}
\renewcommand{\labelitemii}{$\cdot$}

\begin{document}

\begin{center}
How to install KeTCindy(Windows)
\end{center}

\hfill modified\ :\ \today

\begin{enumerate}[\bf\large 1.]

\item Install Cinderella, R and Maxima.
 \begin{itemize}
 \item \url{https://beta.cinderella.de}  (Cinderella)
 \item \url{https://cran.r-project.org}   (R)
 \item \url{https://sourceforge.net/projects/maxima/files}  (Maxima)
 \item \url{https://www.sumatrapdfreader.org/download-free-pdf-viewer.html} (Sumatra)
 \end{itemize}
\hspace*{5mm}Rem) Check they start correctly.

\item Install TeX if any TeX has not been installed.
  \begin{enumerate}[(1)]
  \item TeXLive is recommended.
    \begin{itemize}
    \item Files necessary for KeTCindy are already implemented (2018 or later).
    \end{itemize}
  \item kettex is a light-weight TeXLive.
    \begin{itemize}
    \item Download kettex.zip from\\
    \hspace*{10mm}\url{https://www.dropbox.com/s/fthw4btjqqs33tc/kettex.exe?dl=0}
    \item Double-click it and move kettex to \verb|C:\|.
    \end{itemize}
  \item In case of other TeX, see {\bf 3.}(2).
 \end{enumerate}


\item Install KeTCdindy
  \begin{enumerate}[(1)]
  \item Download ketcindy from CTAN(\url{https://ctan.org})\\
  \hspace*{10mm}Search ketcindy \verb|>| Pack­age ketcindy \verb|>| download
    \begin{itemize}
    \item[Rem)]The latest version can be download from Repository:\\
        \hspace*{5mm}\url{https://github.com/ket­pic/ketcindy}\\
        \hspace*{10mm}Clone or Download \verb|>| Download ZIP
    \item[Rem)]Move the extracted folder to Desktop.
    \end{itemize}
  \item Open ketcindy(-master)/forWindows.
    \begin{itemize}
   \item[Rem)]If you use TeX other than TeXLIve/KeTTeX,
      \begin{itemize}
      \item Open setketcindy.bat with a text editor.
      \item Edit paths in it.
      \end{itemize}
    \end{itemize}
  \item Right click the following batch file setketcindy.bat and select "Run as adiministrator".\\
  \hspace*{10mm}\Ltab{15mm}{KeTTeX} setketcindy.bat\\
  \hspace*{10mm}\Ltab{15mm}{TeXLive} setketcindytexlive.bat\\
  \hspace*{10mm}\Ltab{15mm}{Others} edited setketcindy.bat
   \item[Rem)]In the case of Windows10, unblock the security block.    \begin{itemize}
    \item Contents of scripts will be copied into TeX.
    \item ketcindystyle files will be copied and mktexlsr will be executed.
    \item In Cinderella/PlugIns\\
    \hspace*{5mm}KetcindyPluign.jar will be copied.\\
    \hspace*{5mm}ketcindy.ini will be generated .
    \end{itemize}
    \item Double-click setwork.bat.
    \begin{itemize}
    \item[Rem)]Control-click and select Terminal if necessary. 
    \end{itemize}
    \begin{itemize}
    \item Work directory "ketcindy" will be generated in User's home.
    \item TeX(typeset) will be usually latex,xelatex or pdflatex.
    \item Input the version numbers of R, Maxima, for example 3.4.2,\ 5.37.3.
   \item Contents of “work” will be copied into "ketcindy"
    \item \verb|.ketcindy.conf| will be also generated in User's home.\\
    \hspace*{10mm}You can change the setting of PasthT, Mackc, etc.
    \item Template of "ketcindy.conf" will be also copied to work directory.
    \item Configuration files are read in order of 
      \begin{enumerate}[1)]
      \item ketoutset.txt
      \item ketcindy.conf in User's home
      \item ketcindy.conf in the work folder.
      \end{enumerate}
    \end{itemize}
  \end{enumerate}

\item Test run of KeTCindy
 \begin{enumerate}[(1)]
  \item Double-click "template1basic.cdy" in work directory "ketcindy".\\
  \hspace*{10mm}Then a frame in white appear on the screen.  
  \item Press "Figure" button at the top left, then the final PDF output is displayed. 
    \begin{itemize}
    \item[Rem)]To close the window of Terminal when the process exits :
      \begin{itemize}
      \item Start \verb|Terminal|.\\
      \hspace*{10mm}Preferences > Shell \verb|>| "Colse if the shell exited clearly"
      \end{itemize}
    \item[Rem)]It will be better to delete installer folder "ketcindy(-master)" .
    \end{itemize} 
  \end{enumerate}

\item Set Texworks if necessary. For example, in case of KeTTeX,
  \begin{itemize}
  \item Downloadable from \url{https://github.com/TeXworks/texworks/releases/}.
  \item Launch TeXworks,\\
  \hspace*{10mm}and choose Edit \verb|>| Files verb|>| Preference \verb|>| Typeset.
  \item Push upper + and add\\
  \hspace*{5mm}\verb|C:\kettex\texlive\bin\win32|
  \item Select Xelatex or pdflatex.
  \end{itemize}

\item Install gcc for surface drawing.
  \begin{itemize}
  \item Go to  minGW(\url{http://www.mingw.org}).
  \item Download\\
  \hspace*{10mm}download \verb|>| Install \verb|>| mingw-get-setup.exe
  \item Only \verb|mingw32-base, mingw32-gcc-g++| are needed.
  \end{itemize}

\end{enumerate}

\end{document}